
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - Cover Letter Template
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}
\usepackage{fontspec}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

% set variable name of company and position
\newcommand{\targetCompany}{GitHub}
\newcommand{\targetPosition}{Software Engineer}
\newcommand{\targetWebsite}{Linkedin}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \namesection{}{Kuang-Yu Li}{\href{mailto:kuangyu.li@outlook.com}{kuangyu.li@outlook.com}  | \urlstyle{same}\href{https://github.com/kuangyu0801}{Github/kuangyu0801} | \urlstyle{same}\href{https://www.linkedin.com/in/kuang-yu-li-lumiere}{Linkedin/kuang-yu-li-lumiere}
    }
\hfill \today
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     MAIN COVER LETTER CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The first paragraph of your job application letter should include information on why you are writing. Mention the job you are applying for and where you found the position. If you have a contact at the company, mention the person's name and your connection here.

    \lettercontent{
    Dear {\targetCompany} Recruiter, 
   
	\indent My name is Kuang-Yu Li. I am writing to apply for  {\targetPosition}. I learned about this position via {\targetWebsite}. Currently, I am pursuing a master's degree in Information Technology at the University of Stuttgart in Germany.
I am in my fourth semester and expect to graduate at the end of Feb 2022, and I can be on board at the earliest by Mar 2022.
My background makes me a perfect candidate for the position: I am an experienced developer as an intern in IBM and engineer in MediaTek, a self-motivated learner with solid fundamental knowledge of cloud and web technologies, and a team player with agile practice mindsets. Working as {\targetPosition} at {\targetCompany} would allow me to contribute to {\targetCompany}  while achieving my career goal as a solution architect.
}

% The next section of your cover letter should describe what you have to offer the company. Make strong connections between your abilities and the requirements listed in the job posting. Mention specifically how your skills and experience match the job. Expand on the information in your resume.
% Try to support each statement you make with a piece of evidence. Use several shorter paragraphs or bullets rather than one large block of text, which can be difficult to read and absorb quickly.
%For example 

% Using the knowledge and skills I have acquired in my <DEGREE PROGRAM> combined with my technical abilities I believe I can provide significant value to <COMPANY> while providing me invaluable experience to <PREPARE FOR OR FURTHER CAREER>.
% <RELEVANT LIFE STORY/ WORK/ PROJECT >
% In own projects, my coursework, work as a <PREVIOUS JOB TITLE> I have applied knowledge of <SUBJECT MATTER>.
% <LIST OF SMART SOUNDING SKILLS AND TOOLS>.
% Combining these tools with my interests in <FIELD> issues, I hope to help the <DEPARTMENT> answer questions about the <SUBJECT> behind <FIELD> projects.

\lettercontent{
As an experienced developer, I’m proficient in Java programming with a strong understanding of data structures and algorithms. Moreover, I have extensive industry experience with cloud technologies. In my internship, I’m developing a Node.js software plug-in for an open-source cloud-native IDE, Eclipse Theia, with C++ remote development capabilities on Ubuntu Linux using the SCRUM approach.  I have participated in the full SDLC 4G and 5G Android mobile modem in MediaTek. I firmly believe that my development experience would help me quickly adapt to the new role of position and contribute to both team and company. 
}
    \lettercontent{As a self-motivated learner, I can search resources and organize learning path on my own whenever I encounter knowledge or technologies  that I am not familiar with but are  highly relevant to cloud.  A case in point, one of my tasks as intern in IBM requires me to deploy Eclipse Che as a local Kubernetes cluster, I actively took the courses “Introduction to Kubernetes” from Edx and go through each labs and tutorial. Moreover,  I understand the importance of focusing. In my study,  I carefully took courses that are centric to cloud computing, which includes distributed system , mobile computing, service computing. Furthermore, to combine the theories I learned in class and put them into practice, I choose the software-defined networking  lab. 
I believe continuous learning is crucial to a software engineer as technologies are always evolving.}

    \lettercontent{I grow into a team player from my previous position as firmware developer in MediaTek. 
    I am capable of collaborating effortlessly with developers of different technical and cultural backgrounds, 
    as I have participated in 3 large-scale Android smartphone projects, which involve over 1000 developers around the world. 
    My task in firmware development required me to work hand-in-hand with HW and SW developers in all stages of product development life cycle. }

% Conclude your application letter by thanking the employer for considering you for the position. 

    \lettercontent{Enclosed are my resume and transcript highlighting my education and work experience. 
    I thoroughly believe that my background would allow me to make significant contributions to {\targetCompany}. 
    I'm looking forward to this great opportunity and hope to interview with you regarding the position. 
    I will call your office in a few weeks to see if you could schedule a time to speak with me. Thank you in advance for your time and consideration.}
    
    \vspace{0.3cm}
	
    \closing{Sincerely, \\ Kuang-Yu Li}
%\signature{Kuang-Yu Li}
%    \encl{encl: Resume, Transcripts}  \\ % List your enclosed documents here, comment this out to get rid of the "encl:"

\end{document}
\documentclass[]{article}